---
title: "Prosody: Scaled experiment"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
---


```{r include=FALSE}
library(tidyverse)
library(forcats)
library(lme4)
library(broom.mixed)
```

# Reading in data

```{r}
# setwd("/Users/seantrott/Dropbox/UCSD/Research/IndirectSpeechActs/Prosody/pros_scaled/src/analysis/behavioral/")
df_processed = read_csv("../../../data/processed/behavioral/pros_scaled_processed.csv")
nrow(df_processed)
length(unique(df_processed$subject))

# Filter to just critical stims 
df_critical = df_processed %>%
  # Critical trials
  filter(condition %in% c("statement", "request", "question")) %>%
  # The second of each nested trial (i.e., where participant has a response)
  filter(!is.na(response))


```



## Checking over data

```{r}
table(df_critical$speaker)
length(unique(df_critical$subject))
```

## Exclusion

We exclude participants who identify as non-native speakers:

```{r}
df_critical = df_critical %>%
  filter(Native_Speaker != "No") ## Corrected
nrow(df_critical)
length(unique(df_critical$subject))
```

We also exclude participants with any missing data:

```{r}
# 9 speakers * 12 utterances = 108 items
TOTAL = 108

df_counts = df_critical %>%
  group_by(subject) %>%
  summarise(count = n())

df_exclude = df_counts %>%
  filter(count < TOTAL)

df_critical = df_critical %>%
  filter((subject %in% df_exclude$subject) == FALSE)
nrow(df_critical)
length(unique(df_critical$subject))
```


## Additional preprocessing

```{r}
## Here, we reset condition labels (Request vs. Non-Request)
df_critical$Intent = factor(fct_recode(df_critical$condition,
                             "Request" = "request",
                             "Non-Request" = "statement",
                             "Non-Request" = "question"), levels = c("Non-Request", "Request"))

## Here, we reset response labels (Request vs. Non-Request)
df_critical$Interpretation = factor(df_critical$response, levels = c("Non-Request", "Request"))


## We also create several more indicator variables for ease of plotting and merging
df_critical = df_critical %>%
  mutate(correct = Interpretation == Intent) %>%
  mutate(correct_numeric = as.numeric(correct),
         ## 1 for Request, 0 for Non-Request
         response_numeric = as.numeric(Interpretation) - 1) %>%
  mutate(topic = tolower(topic))

# For merging with norming data
df_critical$topic = fct_recode(df_critical$topic,
                               "temperature" = "temp")


```


## Merge with norming data

```{r}
df_normed = read_csv("../../../data/processed/norming/item_means.csv")

df_merged = df_critical %>%
  inner_join(df_normed, by = c("form", "topic"))

nrow(df_critical)
nrow(df_merged)

df_normed$topic %in% df_merged$topic

```



# Primary analyses

## Q1: Does Intent predict response?

### Descriptive

```{r}
mean(df_merged$correct)

df_merged %>%
  group_by(Intent) %>%
  summarise(mean_request = mean(response_numeric))

df_merged %>%
  group_by(form, Intent) %>%
  summarise(mean_request = mean(response_numeric))

df_merged %>%
  group_by(form) %>%
  summarise(mean_request = mean(response_numeric))

```


### Visualization

```{r}
df_merged %>%
  ggplot(aes(x = form, y = response_numeric, color = Intent)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  theme_minimal() +
  ggtitle("Request interpretations by condition") +
  xlab("Condition") +
  ylab("Percent choosing 'request'") +
  scale_y_continuous(limits = c(0, 1))


df_merged %>%
  ggplot(aes(x = mean_request, 
             y = response_numeric, 
             color = Intent,
             shape = Intent)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 1*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 1*sd(x)/sqrt(length(x))},
                geom= 'pointrange') +
  theme_minimal() +
  ggtitle("Request interpretations by p(request)") +
  xlab("P(request)") +
  ylab("Proportion choosing 'request'") +
  scale_y_continuous(limits = c(0, 1))

ggsave("../../../Figures/exp_scaled_priors.png", dpi = 300)

df_merged %>%
  group_by(mean_request) %>%
  summarise(p_request = mean(response_numeric),
            count = n())
```

### Analysis

We ask whether `Intent` explains variance in `Response`, above and beyond other factors like `Prior request probability` and `Form`.


```{r}

model_full = glmer(data=df_merged, 
                Interpretation ~ Intent + form + mean_request +
                  (1 + Intent | topic) +
             (1 + Intent + mean_request | subject) +
               (1 | speaker),
           control=glmerControl(optimizer="bobyqa"),
         family=binomial())

summary(model_full)

model_no_intent = glmer(data=df_merged, 
                Interpretation ~ form + mean_request +
                  (1 + Intent | topic) +
             (1 + Intent + mean_request | subject) +
               (1 | speaker),
           control=glmerControl(optimizer="bobyqa"),
         family=binomial())


anova(model_full, model_no_intent)

```


We can also visualize the coefficients from this model:

```{r}
df_tidy = broom.mixed::tidy(model_full)

df_tidy %>%
  filter(effect == "fixed") %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = term,
             y = estimate)) +
  geom_point() +
  coord_flip() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_errorbar(aes(ymin = estimate - 2*std.error, 
                    ymax = estimate + 2*std.error), 
                width=.2,
                position=position_dodge(.9)) +
  labs(x = "Predictor",
       y = "Estimate") +
  theme_minimal()
```


## Q2: Which acoustic features predict pragmatic interpretation?

### Load acoustic features data

```{r}
df_audio = read_csv("../../../data/processed/audio/audio_features_scaled_stimuli.csv")
df_audio$label = factor(df_audio$label)

df_audio$condition = fct_recode(df_audio$label,
                            "Request" = "ir",
                            "Non-Request" = "literal")

df_audio$speaker = factor(df_audio$speaker)

df_audio = df_audio %>% 
  group_by(speaker) %>% 
  mutate(mean_f0_z_score = scale(mean_f0),
         duration_f0_z_score = scale(duration_f0),
         range_f0_z_score = scale(range_f0),
         sd_f0_z_score = scale(sd_f0),
         slope_f0_z_score = scale(slope_f0),
         mean_intensity_z_score = scale(mean_intensity),
         sd_intensity_z_score = scale(sd_intensity)
         )
```

### Merge with behavioral data

```{r}

df_audio = df_audio %>%
  select(condition, speaker, stimNum, mean_f0_z_score, duration_f0_z_score, range_f0_z_score,
         sd_f0_z_score, slope_f0_z_score, mean_intensity_z_score, sd_intensity_z_score) %>%
  mutate(speaker = factor(speaker))
nrow(df_audio)

df_merged_audio = df_merged %>%
  mutate(speaker = factor(speaker)) %>%
  inner_join(df_audio, on = c("condition", "speaker", "stimNum"))
nrow(df_merged_audio)

df_merged_audio$form = factor(df_merged_audio$form, levels=c("nonconventional", "conventional"))


```



### Analysis

Now we ask whether adding acoustic features to the model predicts participants' **responses**, above and beyond the variance explained by *form* and *speaker* (and their interaction). 

To do this, we compare each model in turn, successively dropping out different acoustic features.

Random effects include random intercepts for subjects and items. Including a random slope for the effect of form for items (as in the models above) prevents the models from converging. (That said, analysis of these models suggests very similar results.)

### Do the features predict participants' predicted label?

```{r}

model_response_full = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())


summary(model_response_full)


df_tidy = broom.mixed::tidy(model_response_full)

df_tidy %>%
  filter(effect == "fixed") %>%
  ggplot(aes(x = reorder(term, estimate),
             y = estimate)) +
  geom_point() +
  coord_flip() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_errorbar(aes(ymin = estimate - 2*std.error, 
                    ymax = estimate + 2*std.error), 
                width=.2,
                position=position_dodge(.9)) +
  labs(x = "Predictor",
       y = "Estimate") +
  theme_minimal()
```


#### F0 slope

```{r}
model_response_no_slope_interaction = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score +
                      mean_f0_z_score * form +
                      duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_slope = glmer(data = df_merged_audio,
                      Interpretation ~ mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_slope_interaction)
anova(model_response_no_slope_interaction, model_response_no_slope)

```

#### Mean F0

```{r}
model_response_no_mean_f0_interaction = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score * form +
                        mean_f0_z_score +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_mean_f0 = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_mean_f0_interaction)
anova(model_response_no_mean_f0_interaction, model_response_no_mean_f0)

```

#### F0 duration (number of voiced frames)

```{r}
model_response_no_f0_dur_interaction = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_f0_dur = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       range_f0_z_score * form +
                       sd_f0_z_score * form +
                       mean_intensity_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_f0_dur_interaction)
anova(model_response_no_f0_dur_interaction, model_response_no_f0_dur)

```


#### Mean Intensity

```{r}
model_response_no_mean_intensity_interaction = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                       duration_f0_z_score * form +
                       range_f0_z_score * form+
                       sd_f0_z_score * form +
                       mean_intensity_z_score +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())

model_response_no_mean_intensity = glmer(data = df_merged_audio,
                      Interpretation ~ slope_f0_z_score * form +
                        mean_f0_z_score * form +
                        range_f0_z_score * form+
                        sd_f0_z_score * form +
                       duration_f0_z_score * form +
                       sd_intensity_z_score * form +
                        (1 | subject) + 
                        (1 | speaker) +
                        (1 | stimNum),
                       control=glmerControl(optimizer="bobyqa"),
                       family = binomial())
```


```{r}
anova(model_response_full, model_response_no_mean_intensity_interaction)
anova(model_response_no_mean_intensity_interaction, model_response_no_mean_intensity)

```

### Multiple comparisons corrections

```{r}
p1 = anova(model_response_full, model_response_no_slope_interaction)$`Pr(>Chisq)`[2]
p2 = anova(model_response_no_slope_interaction, model_response_no_slope)$`Pr(>Chisq)`[2]
p3 = anova(model_response_full, model_response_no_mean_f0_interaction)$`Pr(>Chisq)`[2]
p4 = anova(model_response_no_mean_f0_interaction, model_response_no_mean_f0)$`Pr(>Chisq)`[2]
p5 = anova(model_response_full, model_response_no_f0_dur_interaction)$`Pr(>Chisq)`[2]
p6 = anova(model_response_no_f0_dur_interaction, model_response_no_f0_dur)$`Pr(>Chisq)`[2]
p7 = anova(model_response_full, model_response_no_mean_intensity_interaction)$`Pr(>Chisq)`[2]
p8 = anova(model_response_no_mean_intensity_interaction, model_response_no_mean_intensity)$`Pr(>Chisq)`[2]

p.adjust(c(p1, p2, p3, p4, p5, p6, p7, p8), method="holm")

```


## Acoustic feature visualizations

```{r include=FALSE}
library(ggridges)
```


(Note: These visualizations were not part of the original pre-registration file.)

```{r}
df_merged_audio %>%
  ggplot(aes(x = duration_f0_z_score,
             y = form,
             fill = Interpretation)) +
  geom_density_ridges2(aes(height = ..density..), 
                       color=gray(0.25), alpha = 0.5, 
                       scale=0.85, size=0.75, stat="density") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = slope_f0_z_score,
             y = form,
             fill = Interpretation)) +
  geom_density_ridges2(aes(height = ..density..), 
                       color=gray(0.25), alpha = 0.5, 
                       scale=0.85, size=0.75, stat="density") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = mean_f0_z_score,
             y = form,
             fill = Interpretation)) +
  geom_density_ridges2(aes(height = ..density..), 
                       color=gray(0.25), alpha = 0.5, 
                       scale=0.85, size=0.75, stat="density") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = form,
             y = duration_f0_z_score,
             fill = Interpretation)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = form,
             y = slope_f0_z_score,
             fill = Interpretation)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = form,
             y = mean_f0_z_score,
             fill = Interpretation)) +
  geom_boxplot() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = form,
             y = duration_f0_z_score,
             color = Interpretation)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = form,
             y = slope_f0_z_score,
             color = Interpretation)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_minimal()

df_merged_audio %>%
  ggplot(aes(x = form,
             y = mean_f0_z_score,
             color = Interpretation)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme_minimal()
```



# Demographics (added to pre-registered file)

The original pre-registered file did not contain a section for reporting participant demographics. That is done here.

```{r}
df_demo = df_merged %>%
  group_by(subject, Gender, Native_Speaker, Age) %>%
  summarise(total_rt = sum(rt) / 1000)

table(df_demo$Gender)
table(df_demo$Native_Speaker)

  
mean(df_demo$Age, na.rm = TRUE)
median(df_demo$Age, na.rm = TRUE)
sd(df_demo$Age, na.rm = TRUE)
range(df_demo$Age, na.rm = TRUE)

## Average time
mean(df_demo$total_rt / 60)
median(df_demo$total_rt / 60)
```

# Final visualizations (added to pre-registered file)

```{r}
df_merged_audio %>%
  ggplot(aes(x = form,
             y = duration_f0_z_score,
             color = Interpretation)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(x = "Form",
       y = "Number of Voiced Frames",
       color = "Interpretation") +
  theme_minimal()

ggsave("../../../Figures/exp_scaled_duration_interpretation.png", dpi = 300)

df_merged_audio %>%
  ggplot(aes(x = form,
             y = slope_f0_z_score,
             color = Interpretation)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(x = "Form",
       y = "F0 Slope",
       color = "Interpretation") +
  theme_minimal()

ggsave("../../../Figures/exp_scaled_f0_slope_interpretation.png", dpi = 300)
```

