---
title: "Analysis of acoustic features: scaled up study"
output:
  html_document:
    toc: yes
    toc_float: yes
---


```{r include=FALSE}
library(tidyverse)
library(forcats)
library(lme4)
library(broom)
```

# Load data

```{r}
# setwd("/Users/seantrott/Dropbox/UCSD/Research/IndirectSpeechActs/Prosody/pros_scaled/src/analysis/audio")
df_audio = read_csv("../../../data/processed/audio/audio_features_scaled_stimuli.csv")

df_audio$label = factor(df_audio$label)
df_audio$form = factor(df_audio$form)

nrow(df_audio)
table(df_audio$speaker, df_audio$label)

length(unique(df_audio$ppt_id))

```

## Remove subjects with less than 24 observations


We also exclude participant 16, who was recorded with a lower-quality laptop microphone. (Note that the exclusion does not really affect the primary outcomes reported.)

```{r}
n_obs = df_audio %>%
  group_by(ppt_id) %>%
  summarise(count = n())

hist(n_obs$count)

complete = n_obs %>%
  filter(count == 24)

## print ppt ids with < 24 observations
n_obs %>%
  filter(count < 24)

## Select only ppts with 24 observations
df_audio_filtered = df_audio %>%
 filter(ppt_id %in% complete$ppt_id)
nrow(df_audio_filtered)

## How many remaining?
length(unique(df_audio_filtered$ppt_id))

## Also remove #16, 
df_audio_filtered = df_audio_filtered %>%
 filter(ppt_id != 16)
length(unique(df_audio_filtered$ppt_id))
unique(df_audio_filtered$ppt_id)
nrow(df_audio_filtered)

```


## Descriptive statistics

```{r}
by_intent = df_audio_filtered %>%
  group_by(label) %>%
  summarise(mean_f0 = mean(mean_f0),
            range_f0 = mean(range_f0),
            sd_f0 = mean(sd_f0),
            duration_f0 = mean(duration_f0),
            slope_f0 = mean(slope_f0),
            mean_intensity = mean(mean_intensity),
            sd_intensity = mean(sd_intensity))

by_intent
```

## Normalize variables by speaker

Now we z-score our variables, by speaker. E.g., for each speaker, we normalize each observation by z-scoring it *to that speaker*.

```{r}
df_audio_filtered = df_audio_filtered %>% 
  group_by(speaker) %>% 
  mutate(mean_f0_z_score = scale(mean_f0),
         duration_f0_z_score = scale(duration_f0),
         range_f0_z_score = scale(range_f0),
         sd_f0_z_score = scale(sd_f0),
         slope_f0_z_score = scale(slope_f0),
         mean_intensity_z_score = scale(mean_intensity),
         sd_intensity_z_score = scale(sd_intensity)
         )

```



# Machine learning classifier

## Do acoustic features help us classify intent overall?

For a first-pass, we recode "statements" and "questions" as non-requests.

```{r}
df_audio_filtered$label_recoded = fct_recode(df_audio_filtered$label,
                                    "non-request" = "statement",
                                    "non-request" = "question")
```



### Logistic regression

```{r}
set.seed(123)

df_audio_filtered$index = c(1: nrow(df_audio_filtered))
prob_outputs = c()
for (iterating_index in c(1:nrow(df_audio_filtered))) {
  
  train = df_audio_filtered %>%
    filter(index != iterating_index)
  
  test = df_audio_filtered %>%
    filter(index == iterating_index)
  
  model_core = glm(data = train,
                  label_recoded ~ 
                    mean_f0_z_score * form + 
                    range_f0_z_score * form + 
                    sd_f0_z_score * form + 
                    duration_f0_z_score * form +
                    slope_f0_z_score * form + 
                    mean_intensity_z_score * form +
                    sd_intensity_z_score * form,
                   family = binomial())

  probabilities = predict(model_core, test, type="response")

  prob_outputs[iterating_index] = probabilities
}


df_audio_filtered$lr_probs = prob_outputs

df_audio_filtered %>%
  ggplot(aes(x = lr_probs,
             fill = label_recoded)) + 
  geom_density(alpha = .6) +
  labs(x = "P(Request)",
       title = "Logistic regression predictions by true label") +
  theme_minimal()


df_audio_filtered$lr_prediction = ifelse(df_audio_filtered$lr_probs > 0.5,
                             "request","non-request")

df_audio_filtered$lr_correct = df_audio_filtered$lr_prediction == df_audio_filtered$label_recoded
mean(df_audio_filtered$lr_correct)
```

We see that a logistic regression classifier equipped with all seven features gives us `r scales::percent(mean(df_audio_filtered$lr_correct))` accuracy on held-out test items.


# Which cues are particularly predictive?

Now, we use nested model comparisons to determine *which cues* are particularly predictive of intent.

## All items


```{r}
  
model_all = glm(data = df_audio_filtered,
                  label_recoded ~ 
                  mean_f0_z_score + range_f0_z_score + sd_f0_z_score + duration_f0_z_score +
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_mean_f0 = glm(data = df_audio_filtered,
                  label_recoded ~ range_f0_z_score + sd_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_range_f0 = glm(data = df_audio_filtered,
                  label_recoded ~ mean_f0_z_score + sd_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_sd_f0 = glm(data = df_audio_filtered,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_duration_f0 = glm(data = df_audio_filtered,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_slope_f0 = glm(data = df_audio_filtered,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_mean_intensity = glm(data = df_audio_filtered,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + slope_f0_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_sd_intensity = glm(data = df_audio_filtered,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + slope_f0_z_score + mean_intensity_z_score,
                   family = binomial())


summary(model_all)

df_broom = broom::tidy(model_all)

df_broom %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = reorder(term, estimate),
             y = estimate)) +
  geom_point() +
  coord_flip() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_errorbar(aes(ymin = estimate - 2*std.error, 
                    ymax = estimate + 2*std.error), 
                width=.2,
                position=position_dodge(.9)) +
  labs(x = "Coefficient estimate",
       y = "Predictor") +
  theme_minimal()


```


### Model comparisons

```{r}
mean_f0 = anova(model_no_mean_f0, model_all)
mean_f0
p_mean_f0 = pchisq(mean_f0$Deviance[2], mean_f0$Df[2], lower.tail = FALSE)
p_mean_f0

range_f0 = anova(model_no_range_f0, model_all)
range_f0
p_range = pchisq(range_f0$Deviance[2], range_f0$Df[2], lower.tail = FALSE)
p_range

sd_f0 = anova(model_no_sd_f0, model_all)
sd_f0
p_sd_f0 = pchisq(sd_f0$Deviance[2], sd_f0$Df[2], lower.tail = FALSE)

duration_f0 = anova(model_no_duration_f0, model_all)
duration_f0
p_duration_f0 = pchisq(duration_f0$Deviance[2], duration_f0$Df[2], lower.tail = FALSE)
p_duration_f0

slope_f0 = anova(model_no_slope_f0, model_all)
slope_f0
p_slope_f0 = pchisq(slope_f0$Deviance[2], slope_f0$Df[2], lower.tail = FALSE)
p_slope_f0

mean_intensity = anova(model_no_mean_intensity, model_all)
mean_intensity
p_mean_intensity = pchisq(mean_intensity$Deviance[2], mean_intensity$Df[2], lower.tail = FALSE)
p_mean_intensity

sd_intensity = anova(model_no_sd_intensity, model_all)
sd_intensity
p_sd_intensity = pchisq(sd_intensity$Deviance[2], sd_intensity$Df[2], lower.tail = FALSE)
p_sd_intensity

```

Now we correct for multiple comparisons:

```{r}
p.adjust(c(p_mean_f0, p_range, p_sd_f0, p_duration_f0, p_slope_f0, 
           p_mean_intensity, p_sd_intensity), method="holm")

```

After correcting for multiple comparisons, only `F0 slope` passes the significance threshold. 


## Conventional items


```{r}
df_conventional = df_audio_filtered %>%
  filter(form == "conventional")

nrow(df_conventional)
  
model_all = glm(data = df_conventional,
                  label_recoded ~ 
                  mean_f0_z_score + range_f0_z_score + sd_f0_z_score + duration_f0_z_score +
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_mean_f0 = glm(data = df_conventional,
                  label_recoded ~ range_f0_z_score + sd_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_range_f0 = glm(data = df_conventional,
                  label_recoded ~ mean_f0_z_score + sd_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_sd_f0 = glm(data = df_conventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_duration_f0 = glm(data = df_conventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_slope_f0 = glm(data = df_conventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_mean_intensity = glm(data = df_conventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + slope_f0_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_sd_intensity = glm(data = df_conventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + slope_f0_z_score + mean_intensity_z_score,
                   family = binomial())


summary(model_all)


df_broom = broom::tidy(model_all)

df_broom %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = reorder(term, estimate),
             y = estimate)) +
  geom_point() +
  coord_flip() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_errorbar(aes(ymin = estimate - 2*std.error, 
                    ymax = estimate + 2*std.error), 
                width=.2,
                position=position_dodge(.9)) +
  labs(x = "Coefficient estimate",
       y = "Predictor") +
  theme_minimal()


```


### Model comparisons

```{r}
mean_f0 = anova(model_no_mean_f0, model_all)
mean_f0
p_mean_f0 = pchisq(mean_f0$Deviance[2], mean_f0$Df[2], lower.tail = FALSE)
p_mean_f0

range_f0 = anova(model_no_range_f0, model_all)
range_f0
p_range = pchisq(range_f0$Deviance[2], range_f0$Df[2], lower.tail = FALSE)
p_range

sd_f0 = anova(model_no_sd_f0, model_all)
sd_f0
p_sd_f0 = pchisq(sd_f0$Deviance[2], sd_f0$Df[2], lower.tail = FALSE)

duration_f0 = anova(model_no_duration_f0, model_all)
duration_f0
p_duration_f0 = pchisq(duration_f0$Deviance[2], duration_f0$Df[2], lower.tail = FALSE)
p_duration_f0

slope_f0 = anova(model_no_slope_f0, model_all)
slope_f0
p_slope_f0 = pchisq(slope_f0$Deviance[2], slope_f0$Df[2], lower.tail = FALSE)
p_slope_f0

mean_intensity = anova(model_no_mean_intensity, model_all)
mean_intensity
p_mean_intensity = pchisq(mean_intensity$Deviance[2], mean_intensity$Df[2], lower.tail = FALSE)
p_mean_intensity

sd_intensity = anova(model_no_sd_intensity, model_all)
sd_intensity
p_sd_intensity = pchisq(sd_intensity$Deviance[2], sd_intensity$Df[2], lower.tail = FALSE)
p_sd_intensity

```

Now we correct for multiple comparisons:

```{r}
p.adjust(c(p_mean_f0, p_range, p_sd_f0, p_duration_f0, p_slope_f0, 
           p_mean_intensity, p_sd_intensity), method="holm")

```

After correcting for multiple comparisons, only `F0 duration` and `mean intensity` pass the significance threshold. `F0 slope`, which was found to be predictive in previous analyses, is no longer significant after correcting for multiple comparisons (before correcting it is marginally significant: `r p_slope_f0`).


## Non-conventional items


```{r}
df_nonconventional = df_audio_filtered %>%
  filter(form == "non-conventional")

nrow(df_nonconventional)
  
model_all = glm(data = df_nonconventional,
                  label_recoded ~ 
                  mean_f0_z_score + range_f0_z_score + sd_f0_z_score + duration_f0_z_score +
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_mean_f0 = glm(data = df_nonconventional,
                  label_recoded ~ range_f0_z_score + sd_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_range_f0 = glm(data = df_nonconventional,
                  label_recoded ~ mean_f0_z_score + sd_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_sd_f0 = glm(data = df_nonconventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + duration_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_duration_f0 = glm(data = df_nonconventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    slope_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_slope_f0 = glm(data = df_nonconventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + mean_intensity_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_mean_intensity = glm(data = df_nonconventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + slope_f0_z_score + sd_intensity_z_score,
                   family = binomial())

model_no_sd_intensity = glm(data = df_nonconventional,
                  label_recoded ~ mean_f0_z_score + range_f0_z_score + sd_f0_z_score + 
                    duration_f0_z_score + slope_f0_z_score + mean_intensity_z_score,
                   family = binomial())


summary(model_all)

df_broom = broom::tidy(model_all)

df_broom %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = reorder(term, estimate),
             y = estimate)) +
  geom_point() +
  coord_flip() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_errorbar(aes(ymin = estimate - 2*std.error, 
                    ymax = estimate + 2*std.error), 
                width=.2,
                position=position_dodge(.9)) +
  labs(x = "Coefficient estimate",
       y = "Predictor") +
  theme_minimal()


```


### Model comparisons

```{r}
mean_f0 = anova(model_no_mean_f0, model_all)
mean_f0
p_mean_f0 = pchisq(mean_f0$Deviance[2], mean_f0$Df[2], lower.tail = FALSE)
p_mean_f0

range_f0 = anova(model_no_range_f0, model_all)
range_f0
p_range = pchisq(range_f0$Deviance[2], range_f0$Df[2], lower.tail = FALSE)
p_range

sd_f0 = anova(model_no_sd_f0, model_all)
sd_f0
p_sd_f0 = pchisq(sd_f0$Deviance[2], sd_f0$Df[2], lower.tail = FALSE)

duration_f0 = anova(model_no_duration_f0, model_all)
duration_f0
p_duration_f0 = pchisq(duration_f0$Deviance[2], duration_f0$Df[2], lower.tail = FALSE)
p_duration_f0

slope_f0 = anova(model_no_slope_f0, model_all)
slope_f0
p_slope_f0 = pchisq(slope_f0$Deviance[2], slope_f0$Df[2], lower.tail = FALSE)
p_slope_f0

mean_intensity = anova(model_no_mean_intensity, model_all)
mean_intensity
p_mean_intensity = pchisq(mean_intensity$Deviance[2], mean_intensity$Df[2], lower.tail = FALSE)
p_mean_intensity

sd_intensity = anova(model_no_sd_intensity, model_all)
sd_intensity
p_sd_intensity = pchisq(sd_intensity$Deviance[2], sd_intensity$Df[2], lower.tail = FALSE)
p_sd_intensity

```

Now we correct for multiple comparisons:

```{r}
p.adjust(c(p_mean_f0, p_range, p_sd_f0, p_duration_f0, p_slope_f0, 
           p_mean_intensity, p_sd_intensity), method="holm")

```


After correcting for multiple comparisons, we see that `F0 mean` and `F0 duration` are significantly predictive of intent.

### Visualizations 

The features that were most predictive in the analyses above were:

- **#voiced frames** (for both)  
- **mean intensity** (for conventional items)
- **mean F0** (for non-conventional items)
- **F0 slope** (marginally predictive for conventional items).

Let's visualize them below:

```{r}
df_audio_filtered %>% 
  ggplot(aes(x = form,
             y = duration_f0_z_score,
             fill = label_recoded)) +
  geom_boxplot() +
  labs(x = "Form",
       y = "#Voiced frames (z-scored)",
       title = "#Voiced frames by Speaker Intent") +
  theme_minimal()

df_audio_filtered %>% 
  ggplot(aes(x = form,
             y = mean_f0_z_score,
             fill = label_recoded)) +
  geom_boxplot() +
  labs(x = "Form",
       y = "Mean F0 (z-scored)",
       title = "Mean F0 by Speaker Intent") +
  theme_minimal()

df_audio_filtered %>% 
  ggplot(aes(x = form,
             y = mean_intensity_z_score,
             fill = label_recoded)) +
  geom_boxplot() +
  labs(x = "Form",
       y = "Mean intensity (z-scored)",
       title = "Mean intensity by Speaker Intent") +
  theme_minimal()


df_audio_filtered %>% 
  ggplot(aes(x = form,
             y = slope_f0_z_score,
             fill = label_recoded)) +
  geom_boxplot() +
  labs(x = "Form",
       y = "F0 slope",
       title = "F0 slope by Speaker Intent") +
  theme_minimal()

```

