---
title: "Analysis of acoustic features: Exploratory"
output:
  html_document:
    toc: yes
    toc_float: yes
---


```{r include=FALSE}
library(tidyverse)
library(forcats)
library(lme4)
library(broom)
library(lmerTest)

```

# Load data

```{r}
# setwd("/Users/seantrott/Dropbox/UCSD/Research/IndirectSpeechActs/Prosody/pros_scaled/src/analysis/audio")
df_audio = read_csv("../../../data/processed/audio/audio_features_final_segment.csv")

df_audio$label = factor(df_audio$intent2)
df_audio$form = factor(df_audio$form)

nrow(df_audio)
table(df_audio$speaker, df_audio$label)

## How many duplicates
df_audio %>% 
  group_by(hash) %>% 
  filter(n()>1)

## Get distinct
df_audio = df_audio %>%
  distinct(hash, .keep_all = TRUE)

nrow(df_audio)

```


## Descriptive statistics

```{r}
by_intent = df_audio %>%
  group_by(form, label) %>%
  summarise(mean_change = mean(overall_change),
            sd_change = sd(overall_change),
            mean_slope = mean(f0_slope),
            sd_slope = sd(f0_slope))

by_intent
```


# Which cues are particularly predictive?

Now, we use nested model comparisons to determine *which cues* are particularly predictive of intent.

## Interaction between form and intent

First, we consider the interaction for each dependent variable.


```{r}

df_audio$form = factor(df_audio$form, levels = c("non-conventional", "conventional"))
model_change = lmer(data = df_audio,
                overall_change ~ intent2 * form +
                    (1 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)


model_reduced = lmer(data = df_audio,
                overall_change ~ intent2 + form +
                    (1 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)

anova(model_change, model_reduced)
summary(model_change)

p_change = anova(model_change, model_reduced)$`Pr(>Chisq)`[2]

model_slope = lmer(data = df_audio,
                f0_slope ~ intent2 * form +
                    (1 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)


model_reduced = lmer(data = df_audio,
                f0_slope ~ intent2 + form +
                    (1 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)

anova(model_slope, model_reduced)
summary(model_slope)

p_slope = anova(model_slope, model_reduced)$`Pr(>Chisq)`[2]



```

Now we correct for multiple comparisons:

```{r}
p.adjust(c(p_change, p_slope), method = "holm")
```


## Subset analysis

We also consider the main effect of `Intent` for conventional and non-conventional items separately.

### Conventional items

```{r}

model_change = lmer(data = filter(df_audio, form == "conventional"),
                overall_change ~ intent2 +
                    (1 +intent2 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)


model_null = lmer(data = filter(df_audio, form == "conventional"),
                overall_change ~ 
                    (1 +intent2 | topic) +
                    (1 +intent2 | speaker),
                 REML = FALSE)

anova(model_change, model_null)
summary(model_change)

p_change = anova(model_change, model_null)$`Pr(>Chisq)`[2]


model_slope = lmer(data = filter(df_audio, form == "conventional"),
                f0_slope ~ intent2 +
                    (1 +intent2 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)


model_null = lmer(data = filter(df_audio, form == "conventional"),
                f0_slope ~ 
                    (1 +intent2 | topic) +
                    (1 +intent2 | speaker),
                 REML = FALSE)

anova(model_slope, model_null)
summary(model_slope)

p_slope = anova(model_slope, model_null)$`Pr(>Chisq)`[2]

```

Now we correct for multiple comparisons:

```{r}
p.adjust(c(p_change, p_slope), method = "holm")
```



### Non-conventional

```{r}

model_change = lmer(data = filter(df_audio, form == "non-conventional"),
                overall_change ~ intent2 +
                    (1 +intent2 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)


model_null = lmer(data = filter(df_audio, form == "non-conventional"),
                overall_change ~ 
                    (1 +intent2 | topic) +
                    (1 +intent2 | speaker),
                 REML = FALSE)

anova(model_change, model_null)
summary(model_change)

p_change = anova(model_change, model_null)$`Pr(>Chisq)`[2]


model_slope = lmer(data = filter(df_audio, form == "non-conventional"),
                f0_slope ~ intent2 +
                    (1 +intent2 | topic) +
                    (1 + intent2 | speaker),
                 REML = FALSE)


model_null = lmer(data = filter(df_audio, form == "non-conventional"),
                f0_slope ~ 
                    (1 +intent2 | topic) +
                    (1 +intent2 | speaker),
                 REML = FALSE)

anova(model_slope, model_null)
summary(model_slope)

p_slope = anova(model_slope, model_null)$`Pr(>Chisq)`[2]

```

Now we correct for multiple comparisons:

```{r}
p.adjust(c(p_change, p_slope), method = "holm")
```



## Visualizations 


```{r}
df_audio %>%
  ggplot(aes(x = form,
             y = f0_slope,
             color = label)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(x = "Form",
       y = "F0 Slope",
       color = "Intent") +
  theme_minimal()

df_audio %>%
  mutate(label = str_to_title(label)) %>%
  ggplot(aes(x = form,
             y = overall_change,
             color = label)) +
  stat_summary (fun = function(x){mean(x)},
                fun.min = function(x){mean(x) - 2*sd(x)/sqrt(length(x))},
                fun.max = function(x){mean(x) + 2*sd(x)/sqrt(length(x))},
                geom= 'pointrange', 
                position=position_dodge(width=0.95)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(x = "Form",
       y = "Degree of Rise (final - initial)",
       title = "Final rise by Form and Intent",
       color = "Intent") +
  theme_minimal()

ggsave("../../../Figures/fig3_overall_change.png", dpi = 300)

```

